\chapter{Methods}
\label{chap:methods}
In the design of a detector the theory must be supplemented by accurate models of the complex interactions in the radiation portal monitor to determine the performance.
Once the performance of a design has been determined a method must be chosen for how to optimize the design to  ensure the best use of the materials while meeting the performance criteria.
Three models of the detector physics are employed; two Monte Carlo based methods and one deterministic method.
The deterministic model, XSDRN, solves a discretized one dimensional Boltzmann transport equation, and is described in \autoref{sec:XSDRNModel}.
Probabilistic models follow the path of individual neutrons with interactions based on the probability of a given event occurring.
Such codes are also known as Monte Carlo models, for which MCNPX (described in \autoref{sec:MCNPXModel}) and GEANT4 (described in \autoref{sec:G4Intro}) are well known examples.
MCNPX is employed for detailed neutronic modeling, while GEANT4 is employed for optical photon simulations and detailed energy deposition calculations.

The optimization of the detector is completed by a genetic algorithm using the XSDRN model to quickly simulate a large number of geometries.
Small perturbations on these geometries are then completed with the MCNPX model to ensure that the results are accurate and that true convergence has been reached.
The genetic algorithm is introduced in \autoref{sec:GAIntro}.

\section{Pulse Height Dissemination}
\label{sec:PulseHeightDiscrm}
\input{methods/PulseHieghtDiscr.}

\section{MCNPX Modeling}
\label{sec:MCNPXModel}
\input{methods/MCNPXModel}

\section{XSDRN Modeling}
\label{sec:XSDRNModel}
\input{methods/XSDRNModel}

\section{GEANT4 Modeling}
\label{sec:G4Intro}
\input{methods/G4Intro}

\section{Genetic Algorithm Introduction}
\label{sec:GAIntro}
\input{methods/GAIntro}