\chapter{Results}
\label{chap:results}

The basis for setting a pulse height discriminator to differentiate between neutron and gammas can be attributed to the secondary electrons and the difference in energy mechanisms as presented later.
However, the application to physical detectors has yet to be concretely formulated.
This section will serve to remedy that and present a pulse height discrimination scheme capable of discrimination between neutrons and gammas.

It is currently understood that the light output per path length in the film (which is directly proportional to the pulses collected on the PMT) is related to the stopping power of the radiation in the film material.
For a given material the stopping power of the film will be constant, and therefore the light output of the film can be found by integrating the light output per path length over the total length of the film.
It is then possible to conclude that the light output of a film is proportional to the energy deposited in the film.

Preferential energy deposition by reaction products from neutron interactions relative to gammas will enhance the discrimination by creating larger neutron light pulses than the gamma pulses, allowing for fewer neutron pulses to be classified as gamma pulses because they are below the MLLD.
Thus, neutron-gamma discrimination can be enhanced by optimizing the energy deposition in the film. 

\section{Energy Deposition}
\input{results/energyDep}

\section{Optimal Detector Designs}

The neutron count rate criteria of 2.5 counts per second per nanogram of \iso[252]{Cf} can be used to estimate the size of a detector needed to meet this criteria for various detector efficiencies. 
If the detector has an intrinsic efficiency of 100\%, that is it records every neutron that passes through it as a count, a square of length \SI{23.4}{\cm} would be have sufficient area.
A square of length \SI{23.4}{\cm} has an area less than the area of this page.
A detector efficiency of 50\% would require double the area (or a side length of \SI{33.1}{\cm}), and a detector with efficiency of 1\% requires an area of a square of length \SI{73.9}{\cm}.
The fabricated polymer films have an intrinsic efficiency on the order of \num{1E-3}, which requires covering a sphere of radius \SI{2.08}{\m} area to fulfill the count rate criteria, which is not physically available.
Alternative usage of the material, such as layering, must then be considered in order to have fulfill the neutron criteria.

\input{results/rpm8Opt}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                      									 %
%                  		  	RPM Light Collection                           %
% 									                                                     %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Light Collection}
There is no assurance that the detectors designed based on interaction rate would be feasible to construct; due to their low light output and opaqueness collecting the light from scintillation events is extremely difficult.  
Additional simulation work then needs to be completed to ensure that a RPM in the layered detector design has a realistic method of collecting the light emitted from the scintillation events.
Light transport modeling provides a way to calculate the performance of such a design while providing insights for the improvement of a detector design.
\input{results/RPMLightCollection}
