\chapter{Theory}
\label{chap:theory}
Detecting radiation utilizing a scintillation detector involves several physical processes, which can be elucidated by imagining a typical interaction in a scintillator.
A neutron incident upon a detector interacts by mostly elastic scattering with the nuclei in the RPM material, slowing down to thermal energies.
Once thermal, the neutron then has a large probability of interaction with a neutron absorber in the RPM, which releases fission products into the material.
These charged fission products then interact with the material by mostly electrostatic attractions, ionizing the matter they pass through, depositing their energy by transferring  energy to the kinetic energy of electrons.
In the case of a gamma interaction, an energetic gamma may scatter elastically off of an electron through Compton scattering, producing electrons large kinetic energies.
For both cases the energetic electrons ionize the matter, producing a cascade of electrons.
The material converts the energetic electrons into excited molecules, which can de-excite through the process of scintillation, producing light.
The photons produced by scintillation can then be collected with a PMT and transformed into an electrical signal.

Effective design of a radiation portal monitor should then be guided by the physics guiding the processes of interest.
The process of the thermalization of the neutrons and nuclear absorptions are discussed in \autoref{sec:NuclearInteractions}.
Next, the charged particle interactions and ranges are discussed in \autoref{sec:InteractionsAndRange}.
The scintillation processes is discussed in \autoref{sec:ScintMechanics}, and is followed by a brief discussion of optics in \autoref{sec:OpticsTheory}.

 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                         %
%                      NUCLEAR INTERACTIONS                          %
%                                                                         %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Nuclear Interaction Mechanisms}
\label{sec:NuclearInteractions}
\input{theory/nuclearInteractions}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                         %
%                      ENERGY SCALE AND RANGES                            %
%                                                                         %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Charged Particle Interactions and Ranges}
\label{sec:InteractionsAndRange}
\input{theory/RangeEnergyTheory}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                         %
%                      SCINTILLATION MECHANICS                            %
%                                                                         %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Scintillation Mechanisms}
\label{sec:ScintMechanics}
\input{theory/scintDetIntro}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                         %
%                      OPTICS and LIGHT TRANSPORT                            %
%                                                                         %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Optics and Light Transport}
\label{sec:OpticsTheory}
\input{theory/optics.tex}